Unions of Balls and Configuration Space

### 2014-08-30 Writing/Final/article.tex
update writing and different path topology

@@

\begin{figure}
	\center{\includegraphics[scale=0.26]{./pics/Torus.png}}
	\caption{\label{fig:Torus} The torus has one connected component($\beta_0$), two circular holes ($\beta_1$,the one in the center and the one in the middle of the "donut"), and one two-dimensional void ($\beta_2$, the inside of the "donut"). Copied from \cite{betti wiki}}
\end{figure}

@@

\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection. By doing so, we got a simple graph that characterize the topology of \emph{C-space}. We would like to call it \emph{Topology Roadmap}. This roadmap can also be used to determine if paths exist between two configurations. An example of such roadmap is shown in Figure \ref{simplifiedgraph}. Filled triangles, along with large balls, are suggesting some large open areas, which is a problem \cite{largeconvex} is trying to address.

@@

  \indent In the worst case of searching a graph, the time is

  \indent fdaaaaaaaaaaaaaaaaaaaaaaaaagfdasgdsfagfdsafdsagdsafdsf

@@

\begin{figure}
	\center{ \includegraphics[scale=0.35]{./pics/AstarSearch.PNG} }
	\caption{\label{Astar}} Using \emph{A*} search algorithm to find an optimal path. We discretize balls to configurations on their boundaries. Thus, successors of a configuration are other boundary configurations of the ball current configuration is in. 
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Conclusions and Future work
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}\label{conclusions}
\indent\indent The results demonstrated with our algorithm are sound for covering the \emph{C-space} and represent the topology.

@@

\indent Our next direction is to study the properties and applications of weighted $\alpha$-shape, especially applications in bioinformatics and chemistry, then extend to high dimensions.

\indent Another direction will be studying the topology using the topology roadmap we constructed. Its value is underestimated in this paper, and I believe we can find more there.

@@

>>>>

\indent While computing the betti number for filed triangles in 2D is not difficult too. Delfinado, et al, \cite{incre_betti} provided an incremental algorithm to compute betti numbers in arbitrary dimensions. In our case, we need only 1st betti number. Its algorithm can be stated as:

\begin{algorithmic}[1]
	\Function {IncrementalBetti}{$\sigma_1, \sigma_2, ..., \sigma_m$}
		\State $\beta_0 = \beta_1 = \beta_2 = 0$
		\For {$i \in $ \emph{0 to m}}
			\If {$\sigma_i$ \emph{belongs to a k-cycle of $K_i$}}
				\State $\beta_k \gets \beta_k + 1$
			\Else
				\State $\beta_{k-1} \gets \beta_{k-1} -1$
			\EndIf
		\EndFor
	\EndFunction 
\end{algorithmic}

where $\sigma_1, \sigma_2, ..., \sigma_m$ is a sequence of simplices, and $K_i = \{ \sigma_1, \sigma_2, ..., \sigma_i \}$.

\indent The proof of correctness of the algorithm can be found in \cite{incre_betti}. \\

@@

\begin{figure}
	\center{\includegraphics[scale=0.28]{./pics/Torus.png}}
	\caption{\label{fig:Torus} The torus has one connected component($\beta_0$), two circular holes ($\beta_1$,the one in the center and the one in the middle of the "donut"), and one two-dimensional void ($\beta_2$, the inside of the "donut"). Copied from \cite{betti wiki}}
\end{figure}

@@

\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, while keep check the 1st betti number of these merged 2-simplices( using the algorithm described in \cite{incre_betti} ), reconnect these retracted points with other ones using their previous connection information. By doing so, we got a simple graph that characterize the topology of \emph{C-space}. We would like to call it \emph{Topology Roadmap}. This roadmap can also be used to determine if paths exist between two configurations. An example of such roadmap is shown in Figure \ref{simplifiedgraph}. Filled triangles, along with large balls, are suggesting some large open areas, which is a problem \cite{largeconvex} is trying to address.

@@

  \indent In the worst case of searching a graph, the time is exponential to the length of the path. but it could be polynomial if the graph is actually a tree.  While breaking a graph into several components, these components form a new graph with much less nodes. Even in the worst case, the search for path between components can be much faster than original graph. Then we search in each components(trees) with smaller size compare to the whole graph. The time cost should be less then search the original graph directly.

@@

\begin{figure}
	\center{ \includegraphics[scale=0.35]{./pics/AstarSearch.PNG} }
	\caption{\label{Astar}} Using \emph{A*} search algorithm to find an optimal path. We discretize balls to configurations on their boundaries. Thus, successors of a configuration are other boundary configurations of the ball current configuration is in. 
\end{figure}

\subsection{Different Homotopy Type Paths }
\indent\indent In last section, we searched the near optimal path between two configurations. Now we will show how to find paths with different homotopy types.

\indent The corresponding start and goal nodes in the simplified graph( Figure \ref{simplifiedgraph} ) is 12 and 21. Searching the graph for all paths will give us paths with different homotopy types. Figure \ref{paths} shows the 8 different paths.

\begin{enumerate}
	\item 12--6--19--10--2--0--4--8--1--20--7--21	
	\item 12--6--19--10--2--0--11--14--21	
	\item 12--6--19--10--2--23--5--17--3--1--8--4--0--11--14--21	
	\item 12--6--19--10--2--23--5--17--3--1--20--7--21	
	\item 12--13--9--3--1--8--4--0--11--14--21	
	\item 12--13--9--3--1--20--7--21	
	\item 12--13--9--3--17--5--23--2--0--4--8--1--20--7--21	
	\item	12--13--9--3--17--5--23--2--0--11--14--21	
\end{enumerate}

\begin{figure}
	{\includegraphics[scale=0.28]{./pics/paths/1.png}}
	{\includegraphics[scale=0.28]{./pics/paths/2.png}}
	{\includegraphics[scale=0.28]{./pics/paths/3.png}}
	{\includegraphics[scale=0.28]{./pics/paths/4.png}}
	{\includegraphics[scale=0.28]{./pics/paths/5.png}}
	{\includegraphics[scale=0.28]{./pics/paths/6.png}}
	{\includegraphics[scale=0.28]{./pics/paths/7.png}}
	{\includegraphics[scale=0.28]{./pics/paths/8.png}}
	\caption{\label{paths} 8 paths with different homotopy types. }
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Conclusions and Future work
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}\label{conclusions}
\indent\indent The results demonstrated with our algorithm are sound for covering the \emph{C-space} and represent the topology.

@@

\indent There are many directions we can go from here.

\indent We can use the topology roadmap to study paths and their topology in C-space. We can analyze the shape of C-space and locate large open area. We can try to use this presentations for nonholonomic motion planning problems.

@@

  \bibitem{incre_betti} Delfinado, Cecil Jose A., and Herbert Edelsbrunner. "An incremental algorithm for Betti numbers of simplicial complexes on the 3-sphere." Computer Aided Geometric Design 12.7 (1995): 771-784.
